### 2016-10-20 paper/evaluation.tex
Updated answer of RQ1

To evaluate the frequency of costly regression tests, we first
compiled the project and test source files, later, we measured the
elapsed time to run the tests via the build system ignoring
non-related tasks (\eg, \emph{javadoc} generation).  We grouped the
resulting time from test executions into four different groups: tests
that ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{normal execution}), five to ten minutes (\emph{long
execution}), and more than ten minutes to execute (\emph{very long
execution}).  Figure~\ref{fig:timecost-barplot} shows the distribution
of subjects per group. It is important to mention that
Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
time: since the subjects were tested in a potentially unstable
revision, some tests may fail, interrupting the execution.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/timecost-barplot/timecost-barplot.pdf}
    \caption{\label{fig:timecost-barplot} \Fix{Subjects grouped by
        elapsed time on test execution ($t$): group A ($t < 1m$), group B
        ($1m \leq t < 5m$), group C ($5m \leq t < 10m$), group D ($10m \leq t$)}}
\end{figure}

>>>>

To evaluate the frequency of time-consuming regression tests, we first
compiled the project and test source files, later, we measured the
elapsed time to run the tests via the build system ignoring
non-related tasks (\eg, \emph{javadoc} generation).  We grouped the
resulting time from test executions into four different groups: tests
that ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{normal execution}), five to ten minutes (\emph{long
execution}), and more than ten minutes to execute (\emph{very long
execution}).  Figure~\ref{fig:timecost-barplot} shows the distribution
of subjects per group. It is important to mention that
Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
time: since the subjects were tested in a potentially unstable
revision, some tests may fail, interrupting the execution.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/timecost-barplot/timecost-barplot.pdf}
    \caption{\label{fig:timecost-barplot} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), normal
    execution ($1m \leq t < 5m$), and long execution ($5m \leq t <
    10m$), very long execution ($10m \leq t$).}
\end{figure}

\Fix{Explain scatter plot}
